Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-21 Paper.tex
Minor genesis block fix.

\section{Wire Protocol}\label{app:wire}
The wire-protocol specifies a network-level protocol for how two peers can communicate. It includes handshake procedures and the means for transfering information such as blocks \& transactions.

@@

$\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 2^{22}, 0, (), 42 \big), (), () \big)$

@@

>>>>

\section{Wire Protocol}\label{app:wire}
The wire-protocol specifies a network-level protocol for how two peers can communicate. It includes handshake procedures and the means for transfering information such as peers, blocks and transactions. Peer-to-peer communications between nodes running Ethereum clients are designed to be governed by a simple wire-protocol making use of existing Ethereum technologies and standards such as RLP wherever practical.

Ethereum nodes may connect to each other over TCP only. Peers are free to advertise and accept connections on any port(s) they wish, however, a default port on which the connection may be listened and made will be 30303.

Though TCP provides a connection-oriented medium, Ethereum nodes communicate in terms of packets. These packets are formed as a 4-byte synchronisation token (0x22400891), a 4-byte "payload size", to be interpreted as a big-endian integer and finally an N-byte RLP-serialised data structure, where N is the aforementioned "payload size". To be clear, the payload size specifies the number of bytes in the packet ''following'' the first 8.

There are a number of different types of payload that may be encoded within the RLP. This ''type'' is always determined by the first entry of the RLP, represented as a scalar:

\begin{tabular*}{\columnwidth}[h]{rlll}
\toprule
\multicolumn{4}{c}{\textbf{00s: Session control}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & \textbf{Expected Reply} & \textbf{Packet Format} \vspace{5pt} \\
0x00 & {\small Hello} & {\small Hello}? & $(\text{0x}00, v \in \mathbb{P}, n \in \mathbb{P}, \mathbf{i} \in \mathbb{B}, c \in \mathbb{P}, p \in \mathbb{P}, i \in \mathbb{B}_{64})$ \\
\midrule
0x01 & {\small Disconnect} & {\small Disconnect}? & $(\text{0x}01, r \in \mathbb{P})$ \\
\midrule
0x02 & {\small Ping} & {\small Pong} & $(\text{0x}02)$ \\
\midrule
0x03 & {\small Pong} && $(\text{0x}03)$ \\
\midrule

\bottomrule
\end{tabular*}

\begin{tabular*}{\columnwidth}[h]{rlll}
\toprule
\multicolumn{4}{c}{\textbf{00s: Information}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & \textbf{Expected Reply} & \textbf{Packet Format} \vspace{5pt} \\
0x10 & {\small GetPeers} & {\small Peers} & $(\text{0x}10)$ \\
\midrule
0x11 & {\small Peers} & & $(\text{0x}11, (a_1 \in \mathbb{B}_4, a_1 \in \mathbb{P}), (), ...)$ \\
\midrule
0x12 & {\small Transactions} & {\small Pong} & $(\text{0x}12)$ \\
\midrule
0x13 & {\small Blocks} && $(\text{0x}13)$ \\
\midrule
0x14 & {\small GetChain} & {\small Chain} & $(\text{0x}14)$ \\
\midrule
0x15 & {\small NotInChain} && $(\text{0x}15)$ \\
\midrule
0x16 & {\small GetTransactions} & {\small Transactions} & $(\text{0x}16)$ \\
\bottomrule
\end{tabular*}

%(0x00, 
%First packet sent over the connection, and sent once by both sides. No other messages may be sent until a Hello is received.
%PROTOCOL_VERSION is one of:
%0x00 for PoC-1;
%0x01 for PoC-2;
%0x07 for PoC-3;
%0x09 for PoC-4.
%NETWORK_ID should be 0.
%CLIENT_ID Specifies the client software identity, as a human-readable string (e.g. "Ethereum(++)/1.0.0").
%LISTEN_PORT specifies the port that the client is listening on (on the interface that the present connection traverses). If 0 it indicates the client is not listening.
%CAPABILITIES specifies the capabilities of the client as a set of flags; presently three bits are used: 0x01 for peers discovery, 0x02 for transaction relaying, 0x04 for block-chain querying.
%NODE_ID is optional and specifies a 512-bit hash, (potentially to be used as public key) that identifies this node.
%Disconnect
%
%[0x01, REASON]
%Inform the peer that a disconnection is imminent; if received, a peer should disconnect immediately. When sending, well-behaved hosts give their peers a fighting chance (read: wait 2 seconds) to disconnect to before disconnecting themselves.
%REASON is an optional integer specifying one of a number of reasons for disconnect:
%0x00 Disconnect requested;
%0x01 TCP sub-system error;
%0x02 Bad protocol;
%0x03 Useless peer;
%0x04 Too many peers;
%0x05 Already connected;
%0x06 Wrong genesis block;
%0x07 Incompatible network protocols;
%0x08 Client quitting.
%Ping
%
%[0x02]
%Requests an immediate reply of Pong from the peer.
%Pong
%
%[0x03]
%Reply to peer's Ping packet.
%GetPeers
%
%[0x10]
%Request the peer to enumerate some known peers for us to connect to. This should include the peer itself.
%Peers
%
%[0x11, [IP1, Port1, Id1], [IP2, Port2, Id2], ... ]
%Specifies a number of known peers. IP is a 4-byte array 'ABCD' that should be interpreted as the IP address A.B.C.D. Port is a 2-byte array that should be interpreted as a 16-bit big-endian integer. Id is the 512-bit hash that acts as the unique identifier of the node.
%Transactions
%
%[0x12, [nonce, receiving_address, value, ... ], ... ]
%Specify (a) transaction(s) that the peer should make sure is included on its transaction queue. The items in the list (following the first item 0x12) are transactions in the format described in the main Ethereum specification.
%Blocks
%
%[0x13, [block_header, transaction_list, uncle_list], ... ]
%Specify (a) block(s) that the peer should know about. The items in the list (following the first item, 0x13) are blocks in the format described in the main Ethereum specification.
%GetChain
%
%[0x14, Parent1, Parent2, ..., ParentN, Count]
%Request the peer to send Count (to be interpreted as an integer) blocks in the current canonical block chain that are children of Parent1 (to be interpreted as a SHA3 block hash). If Parent1 is not present in the block chain, it should instead act as if the request were for Parent2 &c. through to ParentN. If the designated parent is the present block chain head, an empty reply should be sent. If none of the parents are in the current canonical block chain, then NotInChain should be sent along with ParentN (i.e. the last Parent in the parents list). If no parents are passed, then a reply need not be made.
%NotInChain
%
%[0x15, Hash]
%Tell the peer that the given hash was not found in its block chain.
%GetTransactions
%
%[0x16]
%Request the peer to send all transactions currently in the queue. See Transactions.

@@

$\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 2^{22}, 0, (), \mathtt{\tiny SHA3}\big( (42) \big) \big), (), () \big)$

@@

$\mathtt{\tiny SHA3}\big( (42) \big)$ refers to the SHA3 hash of a byte array of length one whose first and only byte is of value 42.
